The {\em Diff} MILP model and PCA for \\ {\em real-time} DNN robustness certification

### 2025-12-03 CAV 2026/experiments.tex
exp + global
new table
something
update the table
updated the table
fixed table

The spread is the average over all cases of the relative distance between the bound and the highest worst-case found for that case.

\begin{table}[h!]
	\centering
	\begin{tabular}{||c||c|c|c|c|c||}\hline\hline
	Benchmark & model & Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ & $\%$ of spread $\downarrow$ \\\hline \hline
	MNIST   & Vhagar & 20.51 & 9.20 & 9.20 & 118 $\%$
    \\
	M-Conv1 & ITNE & 12.77 & 9.41 & 9.41 & 35 $\%$
	\\ 
    TO=1000s & "2v" & {\bf 11.59}  & 9.38 & 9.38 & {\bf 23 $\%$}
    \\\hline \hline

	FMNIST & Vhagar &  $41.52$ & $21.23$ & $21.23$ & 93 $\%$ 
    \\
	F-Conv1  & ITNE &  $27.57$ &  $22.12$ & $22.12$ & 24 $\%$
	\\ 
    TO=1000s & "2v" &  {\bf 23.67} &  $22.31$ &  $22.31$ & {\bf 6 $\%$}
    \\\hline

	FMNIST & Vhagar &  $37.26$ &  $22.00$ & $22.00$ & 72 $\%$
    \\
	F-Conv1  & ITNE &  $24.56$ &  $22.20$ & $22.20$ & 10 $\%$
	\\ 
    TO=14400s & "2v" &    {\bf 22.56} &  $22.32$ &  $22.32$ & {\bf 1 $\%$}
    \\\hline \hline

	CIFAR-10  & Vhagar & does & not & run & 
    \\
	C-Conv1  & ITNE &  & & &
	\\ 
    TO=1000s & "2v" &    & & &
    \\\hline \hline

@@

>>>>

The gap is the average over all cases of the relative distance between the bound and the highest worst-case found for that case.

\iffalse

\begin{table}[h!]
	\centering
	\begin{tabular}{||c||c|c|c|c|c||}\hline\hline
	Benchmark & model & Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ & $\%$ of gap $\downarrow$ \\\hline \hline
	MNIST   & Vhagar & 20.51 & 9.20 & 9.20 & 118 $\%$
    \\
	M-Conv1 & ITNE & 12.77 & 9.41 & 9.41 & 35 $\%$
	\\ 
    TO=1000s & {\em Diff} & {\bf 11.59}  & 9.38 & 9.38 & {\bf 23 $\%$}
    \\\hline \hline

	FMNIST & Vhagar &  $41.52$ & $21.23$ & $21.23$ & 93 $\%$ 
    \\
	F-Conv1  & ITNE &  $27.57$ &  $22.12$ & $22.12$ & 24 $\%$
	\\ 
    TO=1000s & {\em Diff} &  {\bf 23.67} &  $22.31$ &  $22.31$ & {\bf 6 $\%$}
    \\\hline

	FMNIST & Vhagar &  $37.26$ &  $22.00$ & $22.00$ & 72 $\%$
    \\
	F-Conv1  & ITNE &  $24.56$ &  $22.20$ & $22.20$ & 10 $\%$
	\\ 
    TO=14400s & {\em Diff} &    {\bf 22.56} &  $22.32$ &  $22.32$ & {\bf 1 $\%$}
    \\\hline \hline

	CIFAR-10  & Vhagar & does & not & run & -
    \\
	C-Conv1  & ITNE & 28.61 & 11.58 & 11.58 & $33\%$
	\\ 
    TO=1000s & {\em Diff} &  25.93  & 14.43 & 14.43 & $24\%$
	\\
	& {\em 2b+1} &  25.31 & 19.77 & - & $23\%$
	\\
	& Best &  {\bf 23.44}  &  &  & {\bf 16} $\%$
    \\\hline

	CIFAR-10  & Vhagar & does & not & run & -
    \\
	C-Conv1  & ITNE &  & & &
	\\ 
    TO=14400s & {\em Diff} &  {\bf 20.67}  & 19.03 & 19.03 & {\bf 6} $\%$
	\\
	 & {\em 2b+1} &  {\bf }  &  &  & $\%$
    \\\hline \hline

@@

\fi

\begin{table}[h!]
	\centering
	\begin{tabular}{||c||c|c|c||c|c||c|}\hline\hline
	Benchmark & MILP model: & Vhagar &  ITNE & {\em Diff} & {\em 2b+1} & {\em Best} \\\hline \hline
	MNIST-C1  & Bound $\downarrow$ &  20.80 & 12.32 & {11.14} & {\bf 10.95} & 10.85
    \\
	TO=1000s & $\%$ of gap $\downarrow$ & 120$\%$ & 29 $\%$ & {17} $\%$ & {\bf 15} $\%$& 14 $\%$
	\\ \hline
	TO=14400s  & Bound $\downarrow$ & 17.54 & 11.15 & {\bf 10.14} & 10.29 & 10.07
    \\
	 & $\%$ of gap $\downarrow$ &  84$\%$ & 17 $\%$ & {\bf 7} $\%$ & 8 $\%$ & 6 $\%$

    \\\hline \hline

	FMNIST-C1 & Bound $\downarrow$ & 41.52 & 26.61 & {\bf 23.27}  & 24.09 & 22.78
    \\
	TO=1000s & $\%$ of gap $\downarrow$ & 93 $\%$ & 20 $\%$ & {\bf 5} $\%$ & 10 $\%$ & 3 $\%$
    \\\hline

	TO=14400s & Bound $\downarrow$ & 37.26 & 24.06 & {\bf 22.42 } & 23.80 & 22.34
    \\
	 & $\%$ of gap $\downarrow$ & 72 $\%$ &  9 $\%$ & {\bf 1} $\%$ & 9 $\%$ & 0.6 $\%$
    \\\hline \hline

	CIFAR-C1  & Bound $\downarrow$ & ? & 27.15 & 25.94 & {\bf 24.52}& 23.29
    \\
	TO=1000s & $\%$ of gap $\downarrow$ & ? & 28 $\%$ & 24 $\%$& 
	{\bf 20} $\%$ & 15 $\%$
	\\\hline

	TO=14400s  & Bound $\downarrow$ & ? & 22.73 & {\bf 21.77} & 21.81 & 20.38
    \\
	 & $\%$ of gap $\downarrow$ & ? & 12 $\%$ & {\bf 10} $\%$& {\bf 10} $\%$& 5$\%$
		\\\hline \hline

     \end{tabular}
	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation, average over all bounds $\beta_{i,j}$. {\em Best} uses the best between our {\em Diff} and our {\em 2b+1} for each $i,j$. Lower gaps using {\em Best} means that there are cases where {\em Diff} is much better than {\em 2b+1}, and cases where it is the opposite.}
    \label{table.classical}
\end{table}
